Dancing on Water: The Choreography of Sulfur Dioxide Adsorption to Aqueous Surfaces

### 2011-10-19 DensityResults.tex
Responses to the reviewers

One measure of surface activity is the spatial distribution of molecules in the interfacial region. The density distributions of both \wat~and \suldiox~were calculated for the equilibrium MD simulations. The results presented in Figure \ref{fig:density} show both the water (black) and \suldiox~(red) density distributions across the two simulated slabs. As shown, the single \suldiox~in the neat-water system remained at the water slab surface. The \suldiox~in the saturated system accumulated mostly at the surface, but some residual \suldiox~remained well into the bulk water.

@@

The saturated solution simulation results indicate that under the high concentration of \suldiox, the \suldiox~accumulation at the surface is increased. However, unlike the neat-water slab, the saturated slab has a non-zero bulk concentration of \suldiox. The added concentration of \suldiox~creates a layer of molecules bound to the top of the water surface. The center of the \suldiox~density distribution is further into the gas phase than for the neat-water surface with a single-\suldiox~molecule. Because of the limitations of the classical model in accurately reproducing the first hydration shell around the \suldiox, we do not draw specific conclusions about the hydrated surface complex's geometry. However, the surface affinity of the hydrated \suldiox~is well reproduced by both the classical and ab initio methods.\cite{Baer2010}

>>>>

One measure of surface activity is the spatial distribution of molecules in the interfacial region. The density distributions of both \wat~and \suldiox~were calculated for the equilibrium MD simulations. The results presented in Figure \ref{fig:density} show both the water (black) and \suldiox~(red) density distributions, averaged over the two simulated interfaces of each slab. As shown, the single \suldiox~in the neat-water system remained at the water slab surface. The \suldiox~in the saturated system accumulated mostly at the surface, but some residual \suldiox~remained well into the bulk water.

@@

The saturated solution simulation results indicate that under the high concentration of \suldiox, the \suldiox~accumulation at the surface is increased. However, unlike the neat-water slab, the saturated slab has a non-zero bulk concentration of \suldiox. The added concentration of \suldiox~creates a layer of molecules bound to the top of the water surface. The center of the \suldiox~density distribution is further into the gas phase than for the neat-water surface with a single-\suldiox~molecule. Additionally, the water profile is broader in the saturated system. This indicates that water penetrates into the \suldiox~layer, and moves further into the gas phase than under the neat-water conditions. Because of the limitations of the classical model in accurately reproducing the first hydration shell around the \suldiox, we do not draw specific conclusions about the hydrated surface complex's geometry. However, the surface affinity of the hydrated \suldiox~is well reproduced by both the classical and ab initio methods.\cite{Baer2010}
